\documentstyle[hyperref, margin, line]{res_yy}

\hypersetup{backref,pdfpagemode=Full,colorlinks=false,backref}

\addtolength{\oddsidemargin}{-0.45in}
\addtolength{\voffset}{-0.70in}
\addtolength{\textwidth}{1.00in} \addtolength{\textheight}{1.50in}

\renewcommand{\namefont}{\huge}

\def\Cplusplus{{\rm C\raise.5ex\hbox{\small ++}}}
\def\CSharp{{\rm C\raise.5ex\hbox{\small \#}}}

\def\first{{\raise.5ex\hbox{\small st}}}
\def\second{{\raise.5ex\hbox{\small nd}}}
\def\third{{\raise.5ex\hbox{\small rd}}}
\def\fourth{{\raise.5ex\hbox{\small th}}}

\begin{document}

\name{Rohan Mathur}

\address{
phone: (732) 552-6317 \ \ \ \ \ email: rohan@rmathur.com \ \ \ \ \ website: www.rmathur.com \ \ \ \ \ github: mathur
}

\begin{resume}
\section{\textsc{Education}}
\textbf{University of Illinois at Urbana-Champaign} \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ Graduation: May 2017 \\
Majoring in Computer Engineering
\begin{formatb}
  \employer{l}\title{r}\\
  \location{l}\dates{r}\\
  \body\\
\end{formatb}

\section{\textsc{Experience}}

\employer{\textbf{Rithmio}}
\title{Software Engineering Intern}
\location{Champaign, IL}
\dates{Fall 2015}
\begin{position}
Building out Android SDK prototype app for gesture recognition in the context of aiding physical therapy. Work involves integrating and fine tuning current machine learning models and backend data store. App is to be completed by December 2015 and to enter clinical trials by Q1 2016.
\end{position}

\employer{\textbf{University of Illinois Math Department}}
\title{Undergraduate Researcher}
\location{Champaign, IL}
\dates{Fall 2015}
\begin{position}
Working under Professor Richard Sowers to optimize Android devices at the OS level to function as better long-term data collection and high performance calculation devices.
\end{position}

\employer{\textbf{Offerpop}}
\title{Software Engineering Intern}
\location{New York City, NY}
\dates{Summer 2015}
\begin{position}
Enhanced several features of their Django stack working heavily with the Django ORM and data analysis. Re-architected the new Flask microservice backend mainly dealing with building REST APIs, building custom authentication libraries via HTTP headers, and much more.
\end{position}

\employer{\textbf{Somerset County Library System}}
\title{Website Developer}
\location{Bridgewater, NJ}
\dates{2008 -- 2013}
\begin{position}
Developed a new library website on a stack using Drupal. Wrote custom plugins that interface with an eBook management backend, and wrapper for the existing book database.
\end{position}

\begin{formatb}
  \employer{l}\dates{r}\\
  \body\\
\end{formatb}

\section{\textsc{Projects}}

\employer{\textbf{AOKP Custom Android Open Source OS} \small{- Over 11 million installs}}
\title{Lead Developer}
\location{Seattle, Washington}
\dates{2010 -- Present}
\begin{position}
Lead developer of custom Android ROM with greater features, updates, and stability. Work involves heavy device hardware enablement, Linux kernel optimization and hacking, and high performance Android frameworks and application development. \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ http://aokp.co
\end{position}

\employer{\textbf{LG Optmus G Conversion} \small{- Featured on Engadget, The Verge, etc}}
\dates{Spring 2014}
\begin{position}
Tool that re-writes the LG Optmus G phone's partition structure with customized hex-edited Nexus 4 partitions, enabling the LG Optimus G to use the Nexus 4's system software.
\end{position}

\employer{\textbf{Pocket CUMTD} \small{- Over 1,000 downloads}}
\dates{Spring 2015}
\begin{position}
One of the official Android applications for the Champaign-Urbana bus system. Features favorites, notifications of incoming buses, iBeacon integration, and an expansive map view.
\end{position}

\employer{\textbf{QuickTron} \small{- 2nd Place at hackRU 2013 Fall}}
\dates{Fall 2013}
\begin{position}
Android app that utilizes computer vision algorithms to do a real-time scanning and grading of ScanTron multiple choice test answer sheets, and then emails score reports to students.
\end{position}

\employer{\textbf{whiteboard.js} \small{- Top 30 Project at PennApps Winter 2015}}
\dates{Winter 2015}
\begin{position}
Generates a dynamic multi-page website from drawings of a website layout on a whiteboard. Android app captures images of website and uploads it to a server, where computer vision algorithms build and deploy the website.
\end{position}

\section{\textsc{Activities}}

\begin{formatb}
  \employer{l}\title{r}\\
  \body\\
\end{formatb}

\employer{\textbf{IEEE@UIUC Student Chapter}}
\title{Technical Events Director}
\begin{position}
Organize and lead all technical events, ranging from workshops to hardware hackathons.
\end{position}

\employer{\textbf{ACM@UIUC SIGMobile}}
\title{Chair}
\begin{position}
Organize and lead weekly Android app tutorials and competitions for UIUC's ACM chapter.
\end{position}

\employer{\textbf{HackIllinois 2016 Team}}
\title{Hardware Director}
\begin{position}
Director of hardware projects. Leading development of a custom PCB and hardware tutorials.
\end{position}

\employer{\textbf{Reflections|Projections 2015 Technology Conference}}
\title{Staff}
\begin{position}
Built the Android app for the event. Invited guest speakers and assisted with the event logistics.
\end{position}

\begin{formatb}
  \employer{l}\title{r}\\
\end{formatb}

\end{resume}
\end{document}
